\bf Title here

### 2020-08-02 paper/paper.Rmd
use standard quantile function notation

- Layer 1: boxplot geom
  - data: group by $j$ and filter the observations in the group that have count greater than `cutoff = 15`.
  - x: $j$ is mapped to the x-axis
  - y: the statistical transformed index value: $Q_q(I^{\prime}_t)$ is mapped to the y-axis where $Q_q(x)$ finds the $0, 25, 50, 75, 100$th-quantile for the vector $x$ and $I^{\prime}_t$ is the index value of all the searching bases defined in Matrix \ref{eq:data-structure}.

>>>>

- Layer 1: boxplot geom
  - data: group by $j$ and filter the observations in the group that have count greater than `cutoff = 15`.
  - x: $j$ is mapped to the x-axis
  - y: the statistical transformed index value: $Q_{I^{\prime}_t}(q)$ is mapped to the y-axis where $Q_X(q)$, $q = 0, 25, 50, 75, 100$ finds the qth-quantile of $X$ and $I^{\prime}_t$ denotes the index value of all the searching bases defined in Matrix \ref{eq:data-structure}.

### 2020-08-02 paper/paper.tex
use standard quantile function notation

  \begin{itemize}
  \tightlist
  \item
    data: group by \(j\) and filter the observations in the group that
    have count greater than \texttt{cutoff\ =\ 15}.
  \item
    x: \(j\) is mapped to the x-axis
  \item
    y: the statistical transformed index value: \(Q_q(I^{\prime}_t)\) is
    mapped to the y-axis where \(Q_q(x)\) finds the
    \(0, 25, 50, 75, 100\)th-quantile for the vector \(x\) and
    \(I^{\prime}_t\) is the index value of all the searching bases
    defined in Matrix \ref{eq:data-structure}.
  \end{itemize}
\item
  Layer 2: point geom

>>>>

  \begin{itemize}
  \tightlist
  \item
    data: group by \(j\) and filter the observations in the group that
    have count greater than \texttt{cutoff\ =\ 15}.
  \item
    x: \(j\) is mapped to the x-axis
  \item
    y: the statistical transformed index value: \(Q_{I^{\prime}_t}(q)\)
    is mapped to the y-axis where \(Q_X(q)\), \(q = 0, 25, 50, 75, 100\)
    finds the qth-quantile of \(X\) and \(I^{\prime}_t\) denotes the
    index value of all the searching bases defined in Matrix
    \ref{eq:data-structure}.
  \end{itemize}
\item
  Layer 2: point geom
